---
title: "Diamond Price Prediction"
author: "Henry Voelker"
date: "22nd February 2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## General

The Diamond Price Prediction Shiny web app allows to evaluate the "diamond"
dataset from the UsingR package. A linear model is fitted by the app in the
data points. A prediction for user-defined mass (carats) is displayed.

## User Guide
- Use the slider to adjust the user-defined mass (carats).
- Show or hide the linear function visualizing the model fitted.

## Introduction to the Diamond Dataset
```{r loadPackage, results = FALSE, message = FALSE}
library(UsingR)
data(diamond)
```

```{r intro, echo = TRUE}
head(diamond)
```


## Linear Model
A linear model is created in R. The formula refers to y = m * x + n where:

- y = price
- m = "carat" = slope term (increase of price per increase of carats)
- x = mass (carats)
- n = "intercept" term (theoretical price for a 0.00 carat diamond)

```{r linearModel, echo = TRUE}
fit <- lm(price ~ carat, data = diamond)
coef(fit)
```